---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# psych.data.cleanup

<!-- badges: start -->
<!-- badges: end -->

The `psych.data.cleanup` package provides an R interface to retrieve data from surveys containing likert scale questionnaires. It converts all invalid values to identical format, generates a nested object list of descriptive statistics, and print it out to the user. You can visualize the results in the RStudio plot window.

## Installation

You can install the development version of psych.data.cleanup from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("XXinZ28/psych.data.cleanup")
```

## Usage

Given a religious optimism survey data, the `likert_scale_analyzer` function returns a nested list object containing elements that summarizes response counts for each question.

```{r example}
#| warning: false
#| message: false

library(psych.data.cleanup)

likert_results <- likert_scale_analyzer(
  data = religious_som,
  likert_cols = c("relig_q4","relig_q5","relig_q10","relig_q11", "SOM_q1","SOM_q2","SOM_q3"),
  invalid_values = c(" ", "NA")
) 
```

The `draw_graph` function takes in list results from`likert_scale_analyzer` function and displays a series of histograms. 

```{r}
draw_graph(likert_results)
```


