---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# psych.data.cleanup

<!-- badges: start -->
[![R-CMD-check](https://github.com/XXinZ28/psych.data.cleanup/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/XXinZ28/psych.data.cleanup/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/XXinZ28/psych.data.cleanup/graph/badge.svg)](https://app.codecov.io/gh/XXinZ28/psych.data.cleanup)
<!-- badges: end -->

The `psych.data.cleanup` package contains tools for processing survey data containing Likert-scale
questionnaires and visualizing valid response counts. It converts all invalid values to identical format and
generates a nested list of descriptive statistics for each selected question. Visual results appear as faceted
bar charts in the RStudio plot window.

## Installation

You can install the development version of psych.data.cleanup from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("XXinZ28/psych.data.cleanup")
```

## Usage

The `likert_scale_analyzer()` function processes survey data containing Likert-scale questions, and returns a
nested list object with elements that summarize response counts for each question.

```{r example}
#| warning: false
#| message: false

library(psych.data.cleanup)

likert_results <- likert_scale_analyzer(
  data = religious_som,
  likert_cols = c("relig_q4","relig_q5","relig_q10","relig_q11", "SOM_q1","SOM_q2","SOM_q3"),
  invalid_values = c(" ", "NA")
)

likert_results
```

The `draw_graph()` function generates faceted bar charts given the output returned by the
`likert_scale_analyzer()` function. The faceted bar charts display the valid response counts for each of the
selected Likert-scale questions.

```{r}
draw_graph(likert_results)
```
