---
title: "Use the psych_data_cleanup package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use the psych_data_cleanup package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(psych.data.cleanup)
```

## Browsing religious_som

The main function of the psych_data_cleanup package is to let you browse the `religious_som` data in R. We
can accomplish this by first loading the `psych_data_cleanup` package. Then, using the
`likert_scale_analyzer()` function, we can obtain a nested list object containing descriptive statistics for
each selected Likert-scale survey question. We'll retrieve seven columns from `religious_som`, so we'll set the `likert_cols` argument to the names of seven Likert-scale questions within `religious_som`, and the `invalid_values` argument to either empty string, NA, or N/A values.

```{r}
selected_questions <- likert_scale_analyzer(
  data = religious_som,
  likert_cols = c("relig_q4","relig_q5","relig_q10","relig_q11", "SOM_q1","SOM_q2","SOM_q3"),
  invalid_values = c(" ", "NA", "N/A")
) 
```

The `draw_graph()` function takes the nested list object returned by `likert_scale_analyzer()`, and checks
that it is a valid argument belonging to the `Likert_List` class. If the argument does not meet this requirement, an error is thrown. When the argument is a valid object, the `draw_graph()` function produces a series of faceted bar charts displaying the valid response counts for each selected Likert-scale question. The fill color of the bar charts visually differentiates the Likert-scale that corresponds to each question.

```{r}
draw_graph(selected_questions)
```

## Religious Optimism Data

The psych_data_cleanup package also comes with a built-in data set that resembles the responses of a religious
optimism questionnaire.

```{r}
psych.data.cleanup::religious_som
```
